Elephant Seal Age JAE Intraspecific Variation

### 2024-04-25 paper/paperv3.qmd
fixing the semi join

full <- semi_join(resight, sealdat, "animalID") %>% group_by(animalID, calyear) %>% count(calyear)

ggplot(full, aes(calyear, n)) + 
  geom_point()

>>>>

full <- semi_join(resight, sealdat, "animalID") %>% 
  group_by(animalID, calyear) %>% 
  count(calyear) %>% 
  mutate(year = as.numeric(calyear)) %>% 
  filter(year > 1987)

ggplot(full, aes(year, n)) + 
  geom_point()
